### 2019-08-15 thesis.tex
* thesis.tex: Summary: very close to the end

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figD1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

@@

\subsection{The Sun and the near-Earth environment}
\label{sec:sun}
A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. This accessible space physics
laboratory can indeed lead to discoveries that can be applied and extended
to remote cosmic systems. However, the primary reason behind the international
effort\footnote{A complete description, of NASA's missions is available at
\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and
\ref{esa}) on understanding the complex physics of the Sun and interplanetary
space is to unlock means of predicting the occurrence and intensity of solar
activity, and anticipate how the near-Earth environment will be affected.
Reliable forecasting of the space weather is essential for protecting
electronic equipment, radio communications, GPS signal and humans in space
from the effects of the interaction between the dense, magnetized plasma of
coronal mass ejections with the geomagnetic field, and also from the
energetic radiation emitted by solar flares \cite{NAP13060}.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}

>>>>

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figD1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

@@

\subsection{The Sun and the near-Earth environment}
\label{sec:sun}
A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. This accessible space physics
laboratory can indeed lead to discoveries that can be applied and extended
to remote cosmic systems. However, the primary reason behind the international
effort\footnote{A complete description, of NASA's missions is available at
\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and
\ref{esa}) on understanding the complex physics of the Sun and interplanetary
space is to unlock means of predicting the occurrence and intensity of solar
activity, and anticipate how the near-Earth environment will be affected.
Reliable forecasting of the space weather is essential for protecting
electronic equipment, radio communications, GPS signal and humans in space
from the effects of the interaction between the dense, magnetized plasma of
coronal mass ejections with the geomagnetic field, and also from the
energetic radiation emitted by solar flares. Extreme coronal mass ejections
can also cause stronger geomagnetic disturbances that may affect terrestrial
infrastructure such as electric power grids \cite{NAP13060}.
\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}
\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\section{How all of this is related to this work?}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere,
and also the origin of the dangerous solar output disturbing the near-Earth
environment, is the outermost layer of the Sun: the solar corona. The solar
corona can be easily recognized as the bright halo that appears around the
hidden Sun during solar eclipses. \autoref{corona} shows a beautiful
photograph of the corona, taken in the $2017$’s solar eclipse. In the picture,
one can see the moon covering the bright chromosphere, allowing us to have
a glimpse of the thin, but ultra-hot coronal plasma.

\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}
